---
title: "Figure_3"
author: "Sven"
date: "10/7/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Import files:

```{r Import files}

uzdir <- "/Users/sven/Desktop/Project_R_analysis/"
otutable_biom_file <- paste("/Users/sven/Desktop/Project_R_analysis/", "Merged_otu_table_json.biom", sep = "")
map_file <- paste("/Users/sven/Desktop/Project_R_analysis/Sorted_out/", "Modified_mapping_file_mod_with_names_and_variables.txt", sep = "")


```

```{r Create phyloseq object}

# Now import the .biom-formatted otu_table-tax_table file.

biom_otu_tax <- import_biom(otutable_biom_file)

# Add sample data to the dataset using merge
bmsd <- import_qiime_sample_data(map_file)
class(bmsd)
dim(bmsd)
sample_data(bmsd)
sample_variables(bmsd)
biom_otu_tax


#Merge into phyloseq format
Fiord_phyloseq <- merge_phyloseq(biom_otu_tax, bmsd)
Fiord_phyloseq
sample_sums(Fiord_phyloseq)

#Save original phyloseq file
Fiord_phyloseq_v = Fiord_phyloseq

```
##Create average result for multiple rarefaction by transforming data using (divide by 10) and check counts per sample
```{r Create average result for multiple rarefaction by transforming data using (divide by 10), results='markup'}
Fiord_phyloseq = transform_sample_counts(Fiord_phyloseq, function(x) x/10)
sample_sums(Fiord_phyloseq)
```

#### Round and confirm count number
```{r Round and confirm count number, results='markup'}
Fiord_phyloseq = transform_sample_counts(Fiord_phyloseq, round)
sample_sums(Fiord_phyloseq)
Fiord_phyloseq = prune_samples(sample_sums(Fiord_phyloseq)>=1, Fiord_phyloseq)
sample_sums(Fiord_phyloseq)
```

Check that all OTUs have representative counts  
For here taxa = OTU  
__Commands interpretation:__  
_Total number of taxa in dataset:_ sum(taxa_sums(Fiord_phyloseq) > 0)   

_Any taxa with no hits:_ any(taxa_sums(Fiord_phyloseq)== 0)

```{r identify taxa with only zeros, results='markup', echo=TRUE}
sum(taxa_sums(Fiord_phyloseq) > 0)
any(taxa_sums(Fiord_phyloseq)== 0)
sum(taxa_sums(Fiord_phyloseq) == 0)
any(taxa_sums(Fiord_phyloseq) > 1)
sum(taxa_sums(Fiord_phyloseq) > 1)
any(taxa_sums(Fiord_phyloseq) < 1)
sum(taxa_sums(Fiord_phyloseq) < 1)
```

####Prune taxa with less than 1 count and check taxa numbers again
```{r  Save original file and create new file with only present (no zeroes) taxa, results='markup', echo=TRUE}

#Create new file with only present (no zeroes) taxa

Fiord_phyloseq = prune_taxa(taxa_sums(Fiord_phyloseq) > 1, Fiord_phyloseq)
any(sample_sums(Fiord_phyloseq) == 0)
any(sample_sums(Fiord_phyloseq) > 0)
sum(taxa_sums(Fiord_phyloseq) > 0)
any(sample_sums(Fiord_phyloseq) < 1)
sum(taxa_sums(Fiord_phyloseq) < 1)
```

##Compare sequences per sample or OTU
```{r Compare sequences per sample or OTU}
readsumsdf = data.frame(nreads = sort(taxa_sums(Fiord_phyloseq),TRUE), sorted = 1:ntaxa(Fiord_phyloseq), type = "OTU")
readsumsdf = rbind(readsumsdf,data.frame(nreads = sort(sample_sums(Fiord_phyloseq),TRUE),sorted = 1:nsamples(Fiord_phyloseq), type = "Samples"))

title = "Total number of reads"

p = ggplot(readsumsdf, aes(x = sorted, y = nreads)) +
  geom_bar(stat = "identity")

p + ggtitle(title) +
  scale_y_log10() +
  facet_wrap(~type, 1, scales = "free")
```

```{r What sample variables exist in the phyloseq data}
sample_variables(Fiord_phyloseq)
```

```{r Attached OTU ID}
tax_table(Fiord_phyloseq) <- cbind(tax_table(Fiord_phyloseq), OTU=taxa_names(Fiord_phyloseq))
```

```{r Rename Ranks}
colnames(tax_table(Fiord_phyloseq)) = c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species", "OTU")
tax_table(Fiord_phyloseq) =gsub("D_0__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_1__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_2__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_3__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_4__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_5__", "", tax_table(Fiord_phyloseq))
tax_table(Fiord_phyloseq) =gsub("D_6__", "", tax_table(Fiord_phyloseq))

```
```{r Subset}
#Subset to in/out
Fiord_phyloseq_in_out = subset_samples(Fiord_phyloseq, !Sample_type == "Transverse")

```
```{r Other way to import data}
map_file_PCA = paste("/Users/sven/Desktop/Project_R_analysis/Biolog_Analysis","PCA_No_Letters_variables.txt",sep = "") 
map_file_PCA = paste("/Users/sven/Desktop/Project_R_analysis/Biolog_Analysis","PCA_No_transposed.txt",sep = "") 

bmsd_PCA = import_qiime_sample_data("/Users/sven/Desktop/Project_R_analysis/Biolog_Analysis/PCA_No_Letters_variables.txt")
bmsd_PCA = import_qiime_sample_data("/Users/sven/Desktop/Project_R_analysis/Biolog_Analysis/PCA_transposed.txt")

otutable_biom_file_PCA <- paste("/Users/sven/Desktop/Project_R_analysis/", "Merged_otu_table_json.biom", sep = "")
biom_otu_tax_PCA <- import_biom(otutable_biom_file_PCA)



class(bmsd_PCA)
dim(bmsd_PCA)
sample_data(bmsd_PCA)
sample_variables(bmsd_PCA)
class(biom_otu_tax_PCA)
biom_otu_tax_PCA


#Merge into phyloseq format


bmsd_dataframe = data.frame(bmsd_PCA)
bmsd_dataframe_no_name = within(bmsd_dataframe, rm("New_Name")) #remove the new name column

bmsd_dataframe_no_name_NA = na.omit(bmsd_dataframe_no_name)

bmsd_dataframe_no_name_NA_Duin0 = bmsd_dataframe_no_name_NA[-c(13), ]
bmsd_dataframe_no_name_NA_Win0 = bmsd_dataframe_no_name_NA_Duin0[-c(31), ] #remove row 31

is.na(bmsd_dataframe_no_name_NA)

bmsd_rm_Long = bmsd_dataframe_no_name_NA
bmsd_rm_Long[17:32] = list(NULL)
bmsd_rm_long_nocarbon = within(bmsd_rm_Long, rm("Carbon_type"))
```

#Carbon utilisation dissimilarity
```{r Plot dissimialrity based on depth- Ecolog}
library(vegan)
#Attempting to make a new thing. I can't seem to attach the site and in/out to the PCA plot.
write.csv(bmsd_rm_Long,file = "/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/Csv_df.csv")
try_otherwayround = read.csv("/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/Csv_df.csv", row.names = 1)
    write.csv(try_otherwayround,file =
                "/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/try_otherwayround.csv")
    
gettingtedious = within(try_otherwayround, rm("Depth","In_out","Site"))

write.csv(gettingtedious,file = "/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/gettingtedious.csv")

gettingtedious = read.csv("/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/gettingtedious.csv")

#Carry out the bray distance to read the comparisons off of.
Braygt = vegdist(gettingtedious, method = "bray", binary = TRUE)
Braygt

#Import the new dataframe with the bray distances
Bray_plot = read.csv("/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/Bray_plot_depth.csv")

#Import the new dataframe with the bray distances - without Doubtful Sound
Bray_plot_noDo = read.csv("/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/Bray_plot_depth_noDo.csv")

#Set up the list for the variable I'll be doing the shape by
In_out_shapelist = c(In = 0, Out = 15)
library(ggplot2)
#Carry out the plot
braydepth_noDo = ggplot(Bray_plot_noDo, aes(y=Bray_Ecolog, x=Type)) + 
  geom_boxplot() +
  xlab("Sample Region")+
  ylab("Bray-Curtis Distance")+
  ylim(0,0.7)

#Display the plot
braydepth_noDo

dev.copy(png,"Bray_dist_depthdiss",width = 300, height = 300)
dev.off()

```
```{r Plot dissimialrity based on horizontal location - Ecolog}
library(vegan)

Bray_setup_InOut = read.csv("/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/Bray_setup_InOut.csv", row.names = 1)

BrayEcoIO = vegdist(Bray_setup_InOut, method = "bray", binary = TRUE)
BrayEcoIO

Bray_plot_InOut = read.csv("/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/Bray_plot_InOut.csv")

Depth_shapelist = c(m0 = 0, m10 = 15)

#Carry out the plot
Brayin_out_box = ggplot(Bray_plot_InOut, aes(y=Bray_Ecolog, x=Depth)) + 
  geom_boxplot() +
  xlab("Sample Depth (m)")+
  ylab("Bray-Curtis Distance")+
  scale_x_discrete(labels = c(0,10))+
  ylim(0,0.7)

#Display the plot
Brayin_out_box

dev.copy(png,"Bray_dist_inoutdiss",width = 300, height = 300)
dev.off()
```

#Physiochemical parameter dissimilarity
```{r Importing CTD data - thanks Bob}

library(tools)


#import.data is a function that reads each of the files, creates a temp filepath
# and then uses the filepath to read the data into a list
import.data<-function(fileList){
  
  tempFP<-file.path(filePath,fileList)
  tempDF<-read.table(tempFP,sep=",",stringsAsFactors = F,header=T,
                     col.names = c("Temperature","OxygenMgL","OxygenPerSat",
                                   "Fluorescence","Depth","Salinity"))
  
}

filePath<-"/Users/sven/Desktop/Project_R_analysis/CTD_data/From_Bob/ascOutput"#sets up file path where aasc data is stored
mainList<-list()#creates a blank list

#creates a vector of the .asc file names in the target folder that can be used 
#by the import.data function
fileNames<- dir(filePath,pattern="*.asc")

#sapply loops through the fileNames list and applys the import.data fxn
# to each of the files in the target folder. Adds them to a list called
#mainList
mainList<-sapply(fileNames,import.data,simplify = F,USE.NAMES = T)

dataframe = do.call(rbind.data.frame, mainList)

write.csv(dataframe,file = "/Users/sven/Desktop/Project_R_analysis/CTD_data/Analysis/CTD_dataframe.csv")

moddf = read.csv("/Users/sven/Desktop/Project_R_analysis/CTD_data/Analysis/CTD_dataframe.csv")

#remove long sound samples for inout PCA
moddf_adjusted = read.csv("/Users/sven/Desktop/Project_R_analysis/CTD_data/Analysis/Actually_maybe_usefulinout.csv", row.names = 1)
```

```{r Bray for Physiochemical - Depth}
library(vegan)

#Set up large bray dataframe so I can read the distances off of it.

Bray_setup_depth = read.csv("/Users/sven/Desktop/Project_R_analysis/CTD_data/Analysis/Bray_CTD.csv", row.names = 1)

Nosite = within(Bray_setup_depth, rm("In_out", "Depth"))
#Why did I take depth out?

#Carry out the bray distance to read the comparisons off of the console.
Braygt = vegdist(Nosite, method = "bray", binary = F)
Braygt

library(reshape2)
braydf = melt(as.matrix(Braygt))


write.csv(braydf, "/Users/sven/Desktop/Project_R_analysis/CTD_data/Analysis/bray_df.csv")

#Import the new dataframe with the bray distances
Bray_plot = read.csv("/Users/sven/Desktop/Project_R_analysis/CTD_data/Analysis/Bray_plot_no_siteordepth.csv")

#Set up the list for the variable I'll be doing the shape by
In_out_shapelist = c(In = 0, Out = 15)

#Carry out the plot
Braydepth_box = ggplot(Bray_plot, aes(y=Bray_CTD, x=Type)) + 
  geom_boxplot() +
  xlab("Sample Location")+
  ylab("Bray-Kurtis Distance")+
  ylim(0,0.7)

#Display the plot
Braydepth_box

dev.copy(png,"Bray_dist_depthdiss",width = 300, height = 300)
dev.off()
```

```{r CTD dissimialrity based on horizontal location}

CTD_plot_InOut = read.csv("/Users/sven/Desktop/Project_R_analysis/CTD_data/Analysis/CTD_plot_inout.csv")

Depth_shapelist = c("0" = 0, "10" = 15)
Siteshapelist = c(Breaksea = 15, Chalky = 16, Doubtful = 17, Dusky = 18, WetJacket = 0)

#Carry out the plot
Brayinout_box = ggplot(CTD_plot_InOut, aes(y=Bray_CTD, x=Depth, group = Depth)) + 
  geom_boxplot() +
  xlab("Sample Depth (m)") +
  ylab("Bray-Kurtis Distance")+
  ylim(0,0.7)

#Display the plot
Brayinout_box

dev.copy(png,"Bray_dist_inoutdiss",width = 300, height = 300)
dev.off()




```

#Calculate microbial community dissimialrity for comparisons

```{r Calculate microbial community dissimilarity}
#Phyloseq to df
ForBray_df_Genus <- tax_glom(Fiord_phyloseq_in_out, taxrank = 'Genus') %>%#Merge the species at the phylum level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% #Extract abundance data from phyloseq object
  psmelt() #Melt into a df

#Subset by Depth
Bin0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "B" & Sample_Depth == "0" & Sample_type == "in")
Bin10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "B" & Sample_Depth == "10" & Sample_type == "in")
Bout0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "B" & Sample_Depth == "0" & Sample_type == "out") 
Bout10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "B" & Sample_Depth == "10" & Sample_type == "out")

Cin0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "C" & Sample_Depth == "0" & Sample_type == "in")
Cin10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "C" & Sample_Depth == "10" & Sample_type == "in")
Cout0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "C" & Sample_Depth == "0" & Sample_type == "out") 
Cout10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "C" & Sample_Depth == "10" & Sample_type == "out")

Doin0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "Do" & Sample_Depth == "0" & Sample_type == "in")
Doin10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "Do" & Sample_Depth == "10" & Sample_type == "in")
Doout0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "Do" & Sample_Depth == "0" & Sample_type == "out") 
Doout10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "Do" & Sample_Depth == "10" & Sample_type == "out")

Duin0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "Du" & Sample_Depth == "0" & Sample_type == "in")
Duin10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "Du" & Sample_Depth == "10" & Sample_type == "in")
Duout0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "Du" & Sample_Depth == "0" & Sample_type == "out") 
Duout10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "Du" & Sample_Depth == "10" & Sample_type == "out")

Win0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "W" & Sample_Depth == "0" & Sample_type == "in")
Win10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "W" & Sample_Depth == "10" & Sample_type == "in")
Wout0_df_Genus = subset(ForBray_df_Genus, Sample_Site == "W" & Sample_Depth == "0" & Sample_type == "out") 
Wout10_df_Genus = subset(ForBray_df_Genus, Sample_Site == "W" & Sample_Depth == "10" & Sample_type == "out")


#Extract Depth, Site, type, genus, and abundnace.
Bin0_df_Genus = Bin0_df_Genus[,c(3,47,48,49,92)] 
Bin10_df_Genus = Bin10_df_Genus[,c(3,47,48,49,92)]
Bout0_df_Genus = Bout0_df_Genus[,c(3,47,48,49,92)]
Bout10_df_Genus = Bout10_df_Genus[,c(3,47,48,49,92)]

Cin0_df_Genus = Cin0_df_Genus[,c(3,47,48,49,92)] 
Cin10_df_Genus = Cin10_df_Genus[,c(3,47,48,49,92)]
Cout0_df_Genus = Cout0_df_Genus[,c(3,47,48,49,92)]
Cout10_df_Genus = Cout10_df_Genus[,c(3,47,48,49,92)]

Doin0_df_Genus = Doin0_df_Genus[,c(3,47,48,49,92)] 
Doin10_df_Genus = Doin10_df_Genus[,c(3,47,48,49,92)]
Doout0_df_Genus = Doout0_df_Genus[,c(3,47,48,49,92)]
Doout10_df_Genus = Doout10_df_Genus[,c(3,47,48,49,92)]

Duin0_df_Genus = Duin0_df_Genus[,c(3,47,48,49,92)] 
Duin10_df_Genus = Duin10_df_Genus[,c(3,47,48,49,92)]
Duout0_df_Genus = Duout0_df_Genus[,c(3,47,48,49,92)]
Duout10_df_Genus = Duout10_df_Genus[,c(3,47,48,49,92)]

Win0_df_Genus = Win0_df_Genus[,c(3,47,48,49,92)] 
Win10_df_Genus = Win10_df_Genus[,c(3,47,48,49,92)]
Wout0_df_Genus = Wout0_df_Genus[,c(3,47,48,49,92)]
Wout10_df_Genus = Wout10_df_Genus[,c(3,47,48,49,92)]


#Transpose data
trans_Bin0_df_Genus = as.data.frame(t(Bin0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Bin0_df_Genus) = Bin0_df_Genus$Genus
trans_Bin10_df_Genus = as.data.frame(t(Bin10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Bin10_df_Genus) = Bin10_df_Genus$Genus
trans_Bout0_df_Genus = as.data.frame(t(Bout0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Bout0_df_Genus) = Bout0_df_Genus$Genus
trans_Bout10_df_Genus = as.data.frame(t(Bout10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Bout10_df_Genus) = Bout10_df_Genus$Genus

trans_Cin0_df_Genus = as.data.frame(t(Cin0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Cin0_df_Genus) = Cin0_df_Genus$Genus
trans_Cin10_df_Genus = as.data.frame(t(Cin10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Cin10_df_Genus) = Cin10_df_Genus$Genus
trans_Cout0_df_Genus = as.data.frame(t(Cout0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Cout0_df_Genus) = Cout0_df_Genus$Genus
trans_Cout10_df_Genus = as.data.frame(t(Cout10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Cout10_df_Genus) = Cout10_df_Genus$Genus

trans_Doin0_df_Genus = as.data.frame(t(Doin0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Doin0_df_Genus) = Doin0_df_Genus$Genus
trans_Doin10_df_Genus = as.data.frame(t(Doin10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Doin10_df_Genus) = Doin10_df_Genus$Genus
trans_Doout0_df_Genus = as.data.frame(t(Doout0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Doout0_df_Genus) = Doout0_df_Genus$Genus
trans_Doout10_df_Genus = as.data.frame(t(Doout10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Doout10_df_Genus) = Doout10_df_Genus$Genus

trans_Duin0_df_Genus = as.data.frame(t(Duin0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Duin0_df_Genus) = Duin0_df_Genus$Genus
trans_Duin10_df_Genus = as.data.frame(t(Duin10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Duin10_df_Genus) = Duin10_df_Genus$Genus
trans_Duout0_df_Genus = as.data.frame(t(Duout0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Duout0_df_Genus) = Duout0_df_Genus$Genus
trans_Duout10_df_Genus = as.data.frame(t(Duout10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Duout10_df_Genus) = Duout10_df_Genus$Genus

trans_Win0_df_Genus = as.data.frame(t(Win0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Win0_df_Genus) = Win0_df_Genus$Genus
trans_Win10_df_Genus = as.data.frame(t(Win10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Win10_df_Genus) = Win10_df_Genus$Genus
trans_Wout0_df_Genus = as.data.frame(t(Wout0_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Wout0_df_Genus) = Wout0_df_Genus$Genus
trans_Wout10_df_Genus = as.data.frame(t(Wout10_df_Genus[,c(as.numeric(1),as.numeric(2))]))
colnames(trans_Wout10_df_Genus) = Wout10_df_Genus$Genus

#Get mean at Genus level
Bin0_Genus_mean = as.data.frame(sapply(split.default(trans_Bin0_df_Genus, names(trans_Bin0_df_Genus)), rowMeans))
Bin10_Genus_mean = as.data.frame(sapply(split.default(trans_Bin10_df_Genus, names(trans_Bin10_df_Genus)), rowMeans))
Bout0_Genus_mean = as.data.frame(sapply(split.default(trans_Bout0_df_Genus, names(trans_Bout0_df_Genus)), rowMeans))
Bout10_Genus_mean = as.data.frame(sapply(split.default(trans_Bout10_df_Genus, names(trans_Bout10_df_Genus)), rowMeans))

Cin0_Genus_mean = as.data.frame(sapply(split.default(trans_Cin0_df_Genus, names(trans_Cin0_df_Genus)), rowMeans))
Cin10_Genus_mean = as.data.frame(sapply(split.default(trans_Cin10_df_Genus, names(trans_Cin10_df_Genus)), rowMeans))
Cout0_Genus_mean = as.data.frame(sapply(split.default(trans_Cout0_df_Genus, names(trans_Cout0_df_Genus)), rowMeans))
Cout10_Genus_mean = as.data.frame(sapply(split.default(trans_Cout10_df_Genus, names(trans_Cout10_df_Genus)), rowMeans))

Doin0_Genus_mean = as.data.frame(sapply(split.default(trans_Doin0_df_Genus, names(trans_Doin0_df_Genus)), rowMeans))
Doin10_Genus_mean = as.data.frame(sapply(split.default(trans_Doin10_df_Genus, names(trans_Doin10_df_Genus)), rowMeans))
Doout0_Genus_mean = as.data.frame(sapply(split.default(trans_Doout0_df_Genus, names(trans_Doout0_df_Genus)), rowMeans))
Doout10_Genus_mean = as.data.frame(sapply(split.default(trans_Doout10_df_Genus, names(trans_Doout10_df_Genus)), rowMeans))

Duin0_Genus_mean = as.data.frame(sapply(split.default(trans_Duin0_df_Genus, names(trans_Duin0_df_Genus)), rowMeans))
Duin10_Genus_mean = as.data.frame(sapply(split.default(trans_Duin10_df_Genus, names(trans_Duin10_df_Genus)), rowMeans))
Duout0_Genus_mean = as.data.frame(sapply(split.default(trans_Duout0_df_Genus, names(trans_Duout0_df_Genus)), rowMeans))
Duout10_Genus_mean = as.data.frame(sapply(split.default(trans_Duout10_df_Genus, names(trans_Duout10_df_Genus)), rowMeans))

Win0_Genus_mean = as.data.frame(sapply(split.default(trans_Win0_df_Genus, names(trans_Win0_df_Genus)), rowMeans))
Win10_Genus_mean = as.data.frame(sapply(split.default(trans_Win10_df_Genus, names(trans_Win10_df_Genus)), rowMeans))
Wout0_Genus_mean = as.data.frame(sapply(split.default(trans_Wout0_df_Genus, names(trans_Wout0_df_Genus)), rowMeans))
Wout10_Genus_mean = as.data.frame(sapply(split.default(trans_Wout10_df_Genus, names(trans_Wout10_df_Genus)), rowMeans))

#Bind into one df
ForBray_Genus_df_num = rbind(Bin0_Genus_mean, 
                         Bin10_Genus_mean, 
                         Bout0_Genus_mean,
                         Bout10_Genus_mean, 
                         Cin0_Genus_mean, 
                         Cin10_Genus_mean, 
                         Cout0_Genus_mean,
                         Cout10_Genus_mean,
                         Doin0_Genus_mean, 
                         Doin10_Genus_mean, 
                         Doout0_Genus_mean,
                         Doout10_Genus_mean,
                         Duin0_Genus_mean, 
                         Duin10_Genus_mean, 
                         Duout0_Genus_mean,
                         Duout10_Genus_mean,
                         Win0_Genus_mean, 
                         Win10_Genus_mean, 
                         Wout0_Genus_mean,
                         Wout10_Genus_mean)


#Remove excess rows
ForBray_Genus_df_num = ForBray_Genus_df_num[-c(2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38,40),]

ForBray_Genus_df = ForBray_Genus_df_num

#Add sample depth as a column
ForBray_Genus_df$Sample_Depth = c(0,10,0,10,0,10,0,10,0,10,
                                      0,10,0,10,0,10,0,10,0,10)
ForBray_Genus_df$Sample_type = as.factor(c("in","in","out","out",
                                           "in","in","out","out",
                                           "in","in","out","out",
                                           "in","in","out","out",
                                           "in","in","out","out"))
ForBray_Genus_df$Sample_Site = as.factor(c("B","B","B","B",
                                           "C","C","C","C",
                                           "Do","Do","Do","Do",
                                           "Du","Du","Du","Du",
                                           "W","W","W","W"))

```
```{r Carry out micro Bray}
Bray_micro = vegdist(ForBray_Genus_df_num, method = "bray", binary = TRUE)
Bray_micro

#Export and add sample sites in the same order.
write.csv(as.matrix(Bray_micro),file =
                "/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/Bray_Allmicro.csv")


#Import the new dataframe with the bray distances
Bray_df_micro_type = read.csv("/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/Brayplot_allmicro_inout.csv")
Bray_df_micro_depth = read.csv("/Users/sven/Desktop/Project_R_analysis/Microbial_community/Figure_2/Brayplot_allmicro_depth.csv")


```
```{r Plot microbial Bray}
#Carry out the boxplot
braydepth_boxallmicro = ggplot(Bray_df_micro_depth, aes(y=Bray_Distance, x=Sample_type)) + 
  geom_boxplot() +
  xlab("Sample Region")+
  ylab("Bray-Curtis Distance")+
  ylim(0,0.7)

#Display the plot
braydepth_boxallmicro

dev.copy(png,"Bray_dist_depthdiss_allmicro",width = 300, height = 300)
dev.off()

#Carry out the boxplot
braytype_boxallmicro = ggplot(Bray_df_micro_type, aes(y=Bray_Distance, x=as.factor(Depth))) + 
  geom_boxplot() +
  xlab("Sample Depth (m)")+
  ylab("Bray-Curtis Distance")+
  ylim(0,0.7)

#Display the plot
braytype_boxallmicro

dev.copy(png,"Bray_dist_typediss_allmicro",width = 300, height = 300)
dev.off()

```








#Statistics
```{r Microbial community}
write.csv(ForBray_Genus_df, "All_micro.csv")

#Make distance matrix:
Allmicrobes_adonis.dist = dist(cbind(ForBray_Genus_df[,c(1:947)]))

library(vegan)
adonis(Allmicrobes_adonis.dist~
              Sample_Depth,
            data = ForBray_Genus_df, 
            permutations = 999)

adonis(Allmicrobes_adonis.dist~
              Sample_type,
            data = ForBray_Genus_df, 
            permutations = 999)

adonis(Allmicrobes_adonis.dist~
              Sample_Site,
            data = ForBray_Genus_df, 
            permutations = 999)

adonis(Allmicrobes_adonis.dist~
              Sample_Depth *
                Sample_type,
            data = ForBray_Genus_df, 
            permutations = 999)

adonis(Allmicrobes_adonis.dist~
              Sample_Depth *
                Sample_Site,
            data = ForBray_Genus_df, 
            permutations = 999)

adonis(Allmicrobes_adonis.dist~
              Sample_type *
                Sample_Site,
            data = ForBray_Genus_df, 
            permutations = 999)

adonis(Allmicrobes_adonis.dist~
              Sample_Depth *
                Sample_type *
         Sample_Site,
            data = ForBray_Genus_df, 
            permutations = 999)

adonis(Allmicrobes_adonis.dist~
              Sample_Depth *
                Sample_type *
         Sample_Site,
            data = ForBray_Genus_df, 
            permutations = 999)

```
```{r Environmental variables and Carbon utilisation to each other}
library(ade4)
Microbialcommunity_Ecolog_mantel_try = mantel.rtest(Allmicrobes_adonis.dist, Ecolog.dist, nrepet = 9999)
Microbialcommunity_Ecolog_mantel_try #p-value =0.0037 - very bad

Microbialcommunity_CTD_mantel_try = mantel.rtest(Allmicrobes_adonis.dist, CTD.dist, nrepet = 9999)
Microbialcommunity_CTD_mantel_try #p-value =0.506 - very bad
```
